Reasoning Graphically about Quantum Computation

### 2008-02-24 papers/reasoning-graphically/paper.tex
more stuff
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1354 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

\subsection{Bang-Boxes}

Bang-Boxes

@@

\begin{itemize}
\item let the node kinds be denoted by the set $K$
\item given a graph $G$ containing a set of variable nodes $V$ 
  a given node $n$, it's type is written $T_n$,
\end{itemize}

@@

>>>>

\subsection{!-Boxes}

!-Boxes

@@

instantiation of a variable node:

\begin{itemize}
\item let the set of node kinds be denoted $K$
\item given a graph $G$, containing a variable node $x$, where for a
  given non-vaiable node $n$ it's type is written $T_n$, the concrete
  graph is:

$$
\{G[x/]  | x \in V \}
$$

\item

\end{itemize}

@@

By enriching graphs with variable-nodes and banged-boxes, to form
graph-patterns, we have lost the compositionality principle from the
underlying concrete graphs. However, this can be restored and shown to
correspond to the underyling compositionality principle.

Type Expressions: We introduce a new form of type for a pattern
graph. In particular,
